---
title: Analyzing Screening Guidelines Scenarios
author: Christian Testa
output: html_document
---

The following outputs are in measures of infections per 100,000. 

For reference, the assumed population sizes of Louisiana and Massachusetts 
are 2,787,423 and 4,230,601 respectively (assumed from 2015 census estimates).


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
devtools::load_all()
library(dplyr)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(ggrepel)
library(here)
```

```{r define helper fn, echo=FALSE, fig.height=4, fig.width=6}
simulate_annual_and_basecase <- function(theta) {
	intervention_outcomes <- list()
	for (intervention in c('basecase', 'annual', 'msm_annual')) {
		e <- constructSimulationEnvironment(theta)
		modify_simulation_environment_for_an_intervention(e, intervention)
		runSimulation(e)
		intervention_outcomes[[length(intervention_outcomes)+1]] <- 
			extractInterventionStatistics(e, intervention)
	}
	do.call(rbind.data.frame, intervention_outcomes)
}
```

```{r simulate and tidy data, echo = FALSE}

for (state in c('LA', 'MA')) { 

	# This is where we have saved the following computation:
	filepath <- here(paste0("Rmd/interventions/annual_all_or_msm_with_trace/data/", tolower(state), "_df.rds"))

	# If it has been pre-computed, fetch it.
	if (file.exists(filepath)) {
		assign(paste0(tolower(state), "_df"),
					 readRDS(filepath))
	} else {
		# set the number of years to run out the model to 2050
		load_globals(model.end = 115)

		# parametrize the model
		load.start()

		# 25 samples from posterior
		trace <- get(paste0('trace_', tolower(state)))
		trace <- trace[sample.int(nrow(trace), 25),]

		df_list <- list()
		for (iter in 1:nrow(trace)) {

			# get optimized for the model in the specified state.
			theta <- as.numeric(trace[iter,])
			names(theta) <- colnames(trace)

			# simmulate the annual and basecase scenarios getting
			# - prevalent cases, incidents, and number of tests done
			df <- simulate_annual_and_basecase(theta)
			df_list[[length(df_list)+1]] <- cbind.data.frame(sim = iter, df)
		}

		df <- do.call(rbind.data.frame, df_list)
		saveRDS(df, filepath)

		assign(paste0(tolower(state), '_df'), df)
	}
}


for (state in c('LA', 'MA')) { 
	df <- get(paste0(tolower(state), '_df'))
	df <- filter(df, year >= 2015 & year <= 2050) 
	df <- mutate(df, prevalence_per_100000 = prevalent_infections / popsize * 100000,
							 incidence_per_100000 = incidents_per_year / popsize * 100000) %>% 
		select(-c(prevalent_infections, incidents_per_year, tests_per_year, popsize))
	df <- reshape2::melt(df, id.vars = c('sim', 'intervention', 'year'))
	assign(paste0(tolower(state), '_df'), df)
}
```

### Prevalence and Incidence 
### Basecase, Annual, and MSM Annual Screening Scenarios

```{r plot data, fig.width=6, fig.height=3, echo=FALSE}
for (state in c('LA', 'MA')) {
	df <- get(paste0(tolower(state), '_df'))
	df <- filter(df, variable != 'tests_per_year')

	df %>% group_by(intervention, year, variable) %>% 
		dplyr::summarize(high = quantile(value, 0.975,na.rm=T),
							low = quantile(value, 0.025,na.rm=T),
							median = median(value, na.rm=T)) -> df

	plt <- 
		ggplot(
					data = df, 
					mapping = aes(
						x=year, 
						y=median, 
						ymax = high,
						ymin = low,
						color = intervention, 
						fill = intervention,
						linetype=intervention,
						group = intervention)) +
			 geom_line() + 
			 geom_ribbon(alpha=0.3, size=0) + 
			 expand_limits(y=c(0,0)) + 
			 facet_wrap(~variable, scales='free_y') + 
			 ggtitle(statenames[[state]]) + 
			 theme_bw() + 
			 guides(linetype = guide_legend(title='Baseline Rate of Screening'),
							color = guide_legend(title='Baseline Rate of Screening'), 
							fill = guide_legend(title='Baseline Rate of Screening')) + 
			 scale_color_manual(values = c(basecase = 'black', annual = 'red', msm_annual='blue')) +
			 scale_fill_manual(values = c(basecase = 'black', annual = 'red', msm_annual='blue')) +
			 ylab("Infections per 100,000") + 
			 xlab("Year") + 
			 scale_x_discrete(limits = seq(2016, 2026, 2), breaks = seq(2016, 2026, 2)) + 
			 if (state == 'LA') {
				 theme(legend.position = 'none')
			 } else {
				 theme(legend.position = 'bottom')
			 }

	print(plt)
}
```


### Infectious and Noninfectious Prevalence 
### Basecase, Annual, and MSM Annual Screening Scenarios

```{r define helper fn 2, echo=FALSE, fig.width=6, fig.height=4}
extractInterventionStatisticsWithInfectiousness <- function(e, intervention) {
	intervention_start <- min(intervention_years)
	intervention_period <- seq((intervention_start-1)*52-1, model.end*52)

	data.frame(
		intervention = intervention,
		year = intervention_period/52 + model_to_gregorian_difference,
		prevalent_infectious_infections = rowSums(e$sim$out[1+intervention_period, 1+infectious_index]),
		prevalent_noninfectious_infections = rowSums(e$sim$out[1+intervention_period, 1+noninfectious_index]),
		popsize = rowSums(e$sim$out[1+intervention_period, 1+allpop.index])
		)
}

simulate_annual_and_basecase2 <- function(theta) {
	intervention_outcomes <- list()
	for (intervention in c('basecase', 'annual', 'msm_annual')) {
		e <- constructSimulationEnvironment(theta)
		modify_simulation_environment_for_an_intervention(e, intervention)
		runSimulation(e)
		intervention_outcomes[[length(intervention_outcomes)+1]] <- 
			extractInterventionStatisticsWithInfectiousness(e, intervention)
	}
	do.call(rbind.data.frame, intervention_outcomes)
}

for (state in c('LA', 'MA')) { 

	# This is where we have saved the following computation:
	filepath <- here(paste0("Rmd/interventions/annual_all_or_msm_with_trace/data/", tolower(state), "_df2.rds"))

	# If it has been pre-computed, fetch it.
	if (file.exists(filepath)) {
		assign(paste0(tolower(state), "_df2"),
					 readRDS(filepath))
	} else {
		# set the number of years to run out the model to 2050
		load_globals(model.end = 115)

		# parametrize the model
		load.start()

		# 25 samples from posterior
		trace <- get(paste0('trace_', tolower(state)))
		trace <- trace[sample.int(nrow(trace), 25),]

		df_list <- list()
		for (iter in 1:nrow(trace)) {

			# get optimized for the model in the specified state.
			theta <- as.numeric(trace[iter,])
			names(theta) <- colnames(trace)

			# simmulate the annual and basecase scenarios getting
			# - prevalent cases, incidents, and number of tests done
			df <- simulate_annual_and_basecase2(theta)
			df_list[[length(df_list)+1]] <- cbind.data.frame(sim = iter, df)
		}

		df <- do.call(rbind.data.frame, df_list)
		saveRDS(df, filepath)

		assign(paste0(tolower(state), '_df2'), df)
	}
}

for (state in c('LA', 'MA')) { 
	df <- get(paste0(tolower(state), '_df2'))
	df <- filter(df, year >= 2015 & year <= 2050) 
	df <- mutate(df, 
							 infectious_prevalence_per_100000 = prevalent_infectious_infections / popsize * 100000,
							 noninfectious_prevalence_per_100000 = prevalent_noninfectious_infections / popsize * 100000
							 ) %>% 
		select(-c(prevalent_infectious_infections, prevalent_noninfectious_infections, popsize))
	df <- reshape2::melt(df, id.vars = c('sim', 'intervention', 'year'))
	assign(paste0(tolower(state), '_df2'), df)
}

for (state in c('LA', 'MA')) {
	df <- get(paste0(tolower(state), '_df2'))

	df %>% group_by(intervention, year, variable) %>% 
		dplyr::summarize(high = quantile(value, 0.975,na.rm=T),
							low = quantile(value, 0.025,na.rm=T),
							median = median(value, na.rm=T)) -> df

	plt <- 
		ggplot(
					data = df, 
					mapping = aes(
						x=year, 
						ymax=high, 
						ymin=low,
						y=median,
						color = intervention, 
						fill = intervention,
						linetype = intervention)) +
			 geom_line() + 
			 geom_ribbon(alpha=0.3,size=0)+ 
			 expand_limits(y=c(0,0)) + 
			 facet_wrap(~variable, scales='free_y') + 
			 ggtitle(statenames[[state]]) + 
			 theme_bw() + 
			 guides(linetype = guide_legend(title='Baseline Rate of Screening'),
							color = guide_legend(title='Baseline Rate of Screening'),
							fill = guide_legend(title='Baseline Rate of Screening')) + 
			 scale_color_manual(values = c(basecase = 'black', annual = 'red', msm_annual='blue')) +
			 scale_fill_manual(values = c(basecase = 'black', annual = 'red', msm_annual='blue')) +
			 scale_x_discrete(limits = seq(2016, 2026, 2), breaks = seq(2016, 2026, 2)) + 
			 if (state == 'LA') {
				 theme(legend.position = 'none')
			 } else {
				 theme(legend.position = 'bottom')
			 }

	print(plt)
}
```

