---
title: Screening Interventions With Elevated MSM Screening Rates
author: Christian Testa
output: html_document
---

A major point of interest of this project is to estimate the 
potential impact of hypothetical screening interventions 
targeted on the Men Who Have Sex with Men (MSM) population in
comparison to general population focused interventions.

We will use the following metrics to compare the interventions which 
we simulate. 

- Number of Additional Tests
- Number of Incident Cases 
- Number of Prevalent Cases
- Number Needed to Test to Avert One Additional Incident Case
- Number Needed to Test to Avert One Prevalent Case

These metrics will be interpreted as relative to the base case scenario.

Note that the number of tests and number of incident cases are defined as cumulative
measures during the intervention time period, whereas the number of prevalent 
cases is taken as a measure at the last intervention year time-point.

Our interventions will be simulated during a span of 5 years after the data-period, 
2017-2021.

The interventions we will investigate are as follows: 

```{r, echo=FALSE}
devtools::load_all()
print(interventions$longname)
```

```{r}

```

